---
title: "p8105_hw5_js5165"
author: "Jingqi Song"
date: "November 7, 2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
library(tidyverse)
theme_set(theme_bw() + theme(legend.position = "right"))
```

## Problem 1
### Dataset Tidiness

```{r P1 tidiness}
import_file = function(x){read_csv(paste0('./data/p1/', x))}
observ = list.files('./data/p1/', pattern = '*.csv') %>% 
  map(import_file) %>% 
  reduce(rbind) %>% 
  janitor::clean_names() %>% 
  mutate(seq = seq(from=1, to=20, by=1),
         group = ifelse(seq < 11, c('control'), c('exp')),
         sub = rep(1:10, 2),
         id = paste(group, sub, sep = '_')) %>% 
  gather(key = "week", value = "observation", week_1:week_8) %>%
  mutate(week = str_replace(week, "week_", "")) %>% 
  select(id, group, week, observation)
  
```

### P1 PLOT

Now we are making a plot to show observations on each subject over time

```{r P1 plot}
p1_plot = observ %>% 
  ggplot(aes(x = week, y = observation)) + 
  geom_line(aes(colour = group, group = id)) +
    labs(
    title = "Observations Over Time" ,
    x = "Week" ,
    y = "Observations"
    ) +
  theme(legend.position = "right")
p1_plot
```

From the plot we can see the fluctuation of each subjects. But in general values of subjects in experimental group are higher than values observed in control group.

## Problem 2

```{r P2}
homicide = read_csv("./data/homicide-data.csv")%>%
  janitor::clean_names()
```

It is a 52179*12 dataset of murders over the past decade in 50 of the largest American cities. The dataset includes the information of each incident (id, date, state, city, longitude and latitude of where it took place, and deposition), and information of the victim of each incident (name, race, age and gender).

### total number of homicides and the number of unsolved homicides within each city

First, we are going to summarize within cities to obtain the total number of homicides and the number of unsolved homicides.

```{r P2.1 summary}
homicide = homicide  %>% 
  mutate(city_state = paste(city, state, sep = ', ')) 
homicide_count = homicide %>% 
  group_by(city_state) %>% 
  mutate(total_homicide = n()) %>% 
  filter(disposition == 'Closed without arrest' | disposition == 'Open/No arrest') %>% 
  mutate(unsolved_homicide = n()) %>% 
  distinct(city_state, total_homicide, unsolved_homicide)
  
```

Now we are going to estimate the proportion of homicides and get confidence interval for unsolved homicides in Baltimore, MD.
The estimated proportion is 0.6456 with 95% CI(0.6276,0.6632).

```{r P2.2 Baltimore}
homicide_baltimore = homicide_count %>% 
  filter(city_state == 'Baltimore, MD')
  
prop_baltimore = prop.test(homicide_baltimore$unsolved_homicide, homicide_baltimore$total_homicide) %>% 
  broom::tidy() %>% 
  select(estimate, conf.low, conf.high)

save(prop_baltimore, file = "Baltimore.RData")
```

Now let's estimate the proportion of homicides and get confidence interval for each of the cities.
Reorganize from the raw data using map, map2, nest and unnest.

```{r P2.3 All cities}
homicide_all = homicide %>% 
  group_by(city_state) %>% 
  nest() %>% 
  mutate(total = map(.x = data, ~count(.x)),
         unsolved = map(.x = data, ~count(.x %>% 
                       filter(disposition == 'Closed without arrest' | disposition == 'Open/No arrest')))) %>%
  select(city_state, total, unsolved) %>% 
  unnest() %>% 
  rename(total = n, unsolved = n1) 

prop_func = function(x) {
  broom::tidy(x) %>% 
  select(estimate, conf.low, conf.high)
}

prop_all = map2(.x = homicide_all$unsolved, .y = homicide_all$total, ~prop.test(.x, .y))
prop_cities = map_df(.x = prop_all, ~prop_func(.x)) %>% 
  mutate(city_state = homicide_all$city_state) %>% 
  select(city_state, estimate, conf.low, conf.high)
```

We are going to create a plot that shows the estimates and CIs for each city.
We can conclude from the plot that the estimated proportion of Chicago is far higher than the rest of the cities; and Richmond has the lowest estimated proportion.

```{r P2.4 plot}
prop_cities %>% 
  ggplot(aes(x = forcats::fct_reorder(city_state,estimate), y = estimate, color = city_state)) +
  geom_point() +
  geom_errorbar(mapping = aes(ymin = conf.low, ymax = conf.high)) +
  theme(axis.text.x = element_text(angle = 75, size = 7)) +
  labs(
      title = "Estimate and CI of Unsolved Homicides for Each City",
      x = "City",
      y = "Estimated Proportion"
    )
```
